Software Development in Startup Companies: The Green-field Startup Model

### 2013-02-24 article/main.tex
fixed comments version 0.2

Deakins \cite{Deakins2005} designed a new spiral methodology, constructed during a
fieldwork with a developer team that had limited resources managing an 
innovative product in volatile e-commerce environments. This methodology represents a fast 
evolutionary approach experimentation with flexible processes. It aims to obtain
customer's feedback as soon as possible for continuous product improvement.%MUN: 
%<-- rephrase, sentence not parsable CG:fixed
Even in this case the spiral methodology%MUN: which model? CG:fixed
is compliant with the nature of a random, ad-hoc and \textit{evolutionary development approach} (CAT 2). In fact, evolutionary development approaches are typically more 
suitable  for web applications, as confirmed in \cite{Deshpande2001}.
Moreover, they provide practices oriented towards rapid and iterative design with complete freedom 
to the developer team, enabled to operate anywhere within the organization ( 
compliant also to the category.%MUN: <-- the whole paragraph is not that clear to me. Try to start 
%with the category (team is catalyst), then write about Deakins spiral model
%CG: partially fixed, the focus here is on the evolutionary development approach

@@

%------------------------------------------------------------------------------%
\subsection{Pay back of the technical debt}
The initial lack of structures and processes negatively affects the 
performance when the company starts to grow. One of the primary objectives of 
startups is to expand their business into fast growing markets. In fact, if 
successful, the company will face a growth in terms of number of customers, 
employees and product functionalities. Then, the increased complexity arises the 
necessity of controlling the initially chaotic software development environment. 
Under delicate circumstances, where an increased market demand meets a poorly 
engineered product and process,  the development team need to start returning 
the accumulated technical debt. As reported by practitioners, introducing more 
structures, documentation and standard procedures, cause an initial drop-down in 
performance which severity depends on the speed of growth, the amount of 
technical debt and the capacity of the team to absorb it.

>>>>

Deakins \cite{Deakins2005} designed a new spiral methodology, constructed during a
fieldwork with a developer team that had limited resources managing an 
innovative product in volatile e-commerce environments. This methodology represents a fast 
evolutionary approach experimentation with flexible processes. It aims to obtain
customer's feedback as soon as possible for continuous product improvement.%MUN: 
%<-- rephrase, sentence not parsable CG:fixed
Even in this case the spiral methodology%MUN: which model? CG:fixed
is compliant with the nature of a random, ad-hoc and \textit{evolutionary development approach} (CAT2). In fact, evolutionary development approaches are typically more 
suitable  for web applications, as confirmed in \cite{Deshpande2001}.
Moreover, they provide practices oriented towards rapid and iterative design with complete freedom 
to the developer team, enabled to operate anywhere within the organization (compliant also to the category.%MUN: <-- the whole paragraph is not that clear to me. Try to start 
%with the category (team is catalyst), then write about Deakins spiral model
%CG: partially fixed, the focus here is on the evolutionary development approach

@@

%------------------------------------------------------------------------------%
\subsection{Paying back the technical debt}
The initial lack of structures and processes negatively affects the 
performance when the company starts to grow. One of the primary objectives of 
startups is to expand their business into fast growing markets. In fact, if 
successful, the company will face a growth in terms of number of customers, 
employees and product functionalities. Then, the increased complexity arises the 
necessity of controlling the initially chaotic software development environment. 
Under delicate circumstances, where an increased market demand meets a poorly 
engineered product and process,  the development team need to start returning 
the accumulated technical debt. As reported by practitioners, introducing more 
structures, documentation and standard procedures, cause an initial drop-down in 
performance which severity depends on the speed of growth, the amount of 
technical debt and the capacity of the team to absorb it.
